Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-23 manuscript/manuscript.Rmd
fixed the figure thingy, erased old figure versions

```{r}
knitr::opts_chunk$set(cache = TRUE, echo = FALSE, message = FALSE, 
                      warning = FALSE, fig.height=5, fig.width=7.5)
library(tidyverse)
```

@@

\begin{figure}
	\includegraphics[width=\linewidth, height = 0.2\textheight]{Figures/timeseries.png}
\caption{
\label{fig:one timeseries}
tbd
}
\end{figure}

@@

\begin{figure}
    \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\linewidth]{Figures/ep_length.png}
        \caption{Episode lengths}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\linewidth]{Figures/rewards.png}
        \caption{Episode rewards}
    \end{subfigure}
    \caption{
        TBD
    }
    \label{fig:lengths and rewards}
\end{figure}

>>>>

```{r knit_global, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, echo = FALSE, message = FALSE, 
                      warning = FALSE, fig.height=5, fig.width=7.5)
library(tidyverse)
```

@@

@@
